Modern Graph Generators: A Survey

### 2018-08-22 comparison.tex
Sherif Changes
Better explanation of the classiffication

%\paragraph{Erd\"{o}s-R\'{e}nyi} One of the first and still very popular approaches with lots of variations and modifications is the random graph model proposed in~\cite{Erdos:1960}. Given a positive integer $n$ and a probability value $0 \leq p \leq 1$, the graph $G(n,p)$ is an undirected graph on $n$ vertices whose edges are chosen s.t. for all pairs of vertices $u,v$ there is an edge $(u,v)$ with probability $p$.
%
%\paragraph{Barabasi-Albert} The Barabasi-Albert (BA) model~\cite{Barabasi99emergenceScaling} proposes that structure emerges in network topologies as the result of two processes -- growth and preferential attachment. The BA model starts with a small set of nodes and grows the network as nodes and edges are added over time. Preferential attachment is based on the idea that the probability of connecting to a node is proportional to the current degree of that node (i.e., ``the rich get richer'').
%
%\paragraph{HOT} The highly optimized tolerance (HOT)~\cite{PhysRevLett.84.2529} model is introduced  using a ``forest fire'' example as follows: Suppose we have a forest which is prone to forest fires. Each portion of the forest has a different chance of starting the fire. We wish to minimize the damage by assigning (a limited amount of) resources such as firebreaks at different positions in the forest. More precisely, we have $n$ possible events, each with an associated probability $p_i, 1 \le i \le n$. Each event can lead to some loss $l_i$, which is a function of the resources $r_i$ allocated for that event $(l_i = f (r_i))$, whose total number is limited ($\sum_i r_i \le R$ for some given $R$). The aim is to minimize the expected cost $\sum_i p_i l_i$. The authors show that resource placement is related to the probability distribution $p_i$ by a power law and the probability of events which cause a loss greater than some value $k$ is related to $k$ by a power law too.
%
%
%\paragraph{R-MAT} The R-MAT (Recursive MATrix)~\cite{DBLP:conf/sdm/ChakrabartiZF04} model can be used to create graphs with community structure, power law degree distributions, and a small diameter. It generates weighted, directed and bipartite graphs. Graph generation is modeled with a matrix recursion procedure in which the adjacency matrix (empty at the beginning) is recursively subdivided into four equal-sized partitions and edges are distributed across the partitions with unequal probabilities.

@@

We decided to classify the generators primarily on the basis of the respective application domains or communities. In Tables~\ref{tab:comparisonCharacteristicsA},~\ref{tab:comparisonCharacteristicsB}   we overview the key characteristics of the data generators clustered according to the respective application domains. In particular, we show:

@@

\begin{sidewaystable}
\scriptsize
\centering
\tbl{Key characteristics of the generators (part A)} {
\begin{tabular}{| c | p{2.2cm} | p{2cm} |  p{2.2cm} | l |  l | l | p{3cm} | p{1.4cm} | l | }
 \hline
           &   & \multicolumn{2}{c}{\textbf{Domain}}
               & \multicolumn{2}{|c|}{\textbf{Operations}}
               & \multicolumn{4}{c|}{\textbf{Configuration}}
               \\ \hline
           &  \textbf{Generator}
               & \textbf{Type}
               & \textbf{Target / sample}
               & \textbf{Read}
               & \textbf{Update}
               & \textbf{\rot{Properties}}
               & \textbf{Distributions}
			   & \textbf{Output format}
               & \textbf{\rot{Distributed\ }}
               \\ \hline
\hline   % ====================== general graphs
\multirow{8}{*}{\rot{\textbf{General}}}
  & graph500  & fixed & & Y & N & Y & power-law & &  Y  \\
\cline{2-10}
   & R-MAt & fixed & & Y & N & Y & power-law & &  N  \\
\cline{2-10}
  & Watts-Strogatz~\cite{watts1998collective} & fixed & & Y & N & Y &  & &  N  \\
\cline{2-10}
  & Preferential Attachment~\cite{barabasi1999emergence} & fixed & & Y & N & Y &  & &  N  \\
\cline{2-10}
  & & & & & & & &  &   \\
\hline
\hline %  ======================  Semantic web
\multirow{22}{*}{\rot{\textbf{Semantic web}}}
 & LUBM & fixed & university  & fixed & N & Y & random (LCG) &  RDF & N   \\
\cline{2-10}
 & LBBM & extracted & Lehigh University BibTeX  & N & N & Y & Monte Carlo &  RDF & N   \\
\cline{2-10}
 & UOBM & fixed & university  & fixed & N & Y & random &  RDF & N   \\
\cline{2-10}
 & IIMB & fixed & movies  & N & N & Y & random &  RDF & N   \\
\cline{2-10}
 & BSBM & fixed & e-commerce  & fixed & N & Y & mostly normal &  RDF, relational & N   \\
\cline{2-10}
 & SP$^2$Bench & fixed & DBLP  & fixed & N & Y & based on DBLP  & RDF & N   \\
\cline{2-10}
 & \cite{Duan:2011:AOC:1989323.1989340} & extracted & -- & N & Y &N & -- &  RDF & N    \\
\cline{2-10}
 & DBPSB & extracted & DBpedia &  templates & N & Y & random &  RDF & N   \\
\cline{2-10}
 & LODIB & fixed & e-commerce &  N & N & Y & 44 types &  RDF & N   \\
\cline{2-10}
 & SIB & fixed & social network &  mixes & mix & Y & from real-world data &  RDF & N   \\
\cline{2-10}
 & Geographica & fixed & OpenStreetMap  & fixed + templates  & N & Y & -- &  RDF & N   \\
\cline{2-10}
 & WatDiv & schema-driven & user-defined  & templates & N & Y & uniform, normal, Zipfian &  RDF & N   \\
\cline{2-10}
 & RBench & extracted & DBLP, Yago  & templates & N & Y & from real-world data &  RDF & N  \\
\cline{2-10}
 & LDBC SPB & fixed & media  & mixes & N & Y & power law, skewed values, value correlation &  RDF & N  \\
\cline{2-10}
 & LinkGen & & & & & & & & \\
\hline
\end{tabular} }
\label{tab:comparisonCharacteristicsA}
\end{sidewaystable}

\begin{sidewaystable}
\scriptsize
\centering
\tbl{Key characteristics of the generators (part B)} {
\begin{tabular}{| c | p{2.2cm}| p{2cm} |  p{2.2cm} | l |  l | l | p{3cm} | p{1.4cm} | l | }
 \hline
           &   & \multicolumn{2}{c}{\textbf{Domain}}
               & \multicolumn{2}{|c|}{\textbf{Operations}}
               & \multicolumn{4}{c|}{\textbf{Configuration}}
               \\ \hline
           &  \textbf{Generator}
               & \textbf{Type}
               & \textbf{Target / sample}
               & \textbf{Read}
               & \textbf{Update}
               & \textbf{\rot{Properties}}
               & \textbf{Distributions}
			   & \textbf{Output format}
               & \textbf{\rot{Distributed\ }}
               \\ \hline
\hline  % ======================  graph databases
\multirow{7}{*}{\rot{\textbf{Graph DBs}}}
 & XGDBench & fixed  & social network  & fixed & Y & Y & power-law &  MAG &  Y  \\
 \cline{2-10}
& graphGen & pattern-driven (Cypher schema) & user-defined  & -- & -- & Y & -- &  property graphs & N   \\
 \cline{2-10}
 & gMark & schema-driven (internal schema) &  user-defined  & generated &  N  & Y & uniform, normal, zipfian &  N-triples & N    \\
\hline
\hline %  ======================   social networks
\multirow{9}{*}{\rot{\textbf{Social networks}}}
& LDBC SNB  & Y & Y &   generated &  & Y & Facebook-like &  CSV, RDF & Y     \\
\cline{2-10}
& S3G2 & Y & Y  & N &  & Y & Facebook-like  &  CSV, RDF & Y   \\
\cline{2-10}
& SNG  & Y & Y &   N &  & Y & power-law & ? &  ?   \\
\cline{2-10}
& Forest Fire  & N & Y   & N &  & N & power-law &  ? & N   \\
\cline{2-10}
& Darwini  & N & N &   N &  & N & user-defined &  ? & Y   \\
\cline{2-10}
& BTER  & N & N &   N &  & N & user-defined &  ? & Y  \\
\cline{2-10}
  & & & & & & & & &    \\
\cline{2-10}
  & & & & & & & & &    \\
\cline{2-10}
  & & & & & & & & &    \\
\hline
\hline   % ======================   graph analytics
\multirow{5}{*}{\rot{\textbf{Analytics}}}
  & & & & & & & & &    \\
\cline{2-10}
  & & & & & & & & &    \\
\cline{2-10}
  & & & & & & & & &    \\
\cline{2-10}
  & & & & & & & & &    \\
\cline{2-10}
  & & & & & & & &  &   \\
\hline
\hline   %  ======================  streaming 
\multirow{5}{*}{\rot{\textbf{Streaming}}}
  & & & & & & & & &    \\
\cline{2-10}
  & & & & & & & & &    \\
\cline{2-10}
  & & & & & & & & &    \\
\cline{2-10}
  & & & & & & & & &    \\
\cline{2-10}
  & & & & & & & &  &   \\
\hline
\end{tabular} }
\label{tab:comparisonCharacteristicsB}
\end{sidewaystable}

>>>>

%\paragraph{Erd\"{o}s-R\'{e}nyi} One of the first and still very popular approaches with lots of variations and modifications is the random graph model proposed in~\cite{Erdos:1960}. Given a positive integer $n$ and a probability value $0 \leq p \leq 1$, the graph $G(n,p)$ is an undirected graph on $n$ vertices whose edges are chosen s.t. for all pairs of vertices $u,v$ there is an edge $(u,v)$ with probability $p$.
%
%\paragraph{Barabasi-Albert} The Barabasi-Albert (BA) model~\cite{Barabasi99emergenceScaling} proposes that structure emerges in network topologies as the result of two processes -- growth and preferential attachment. The BA model starts with a small set of nodes and grows the network as nodes and edges are added over time. Preferential attachment is based on the idea that the probability of connecting to a node is proportional to the current degree of that node (i.e., ``the rich get richer'').
%
%\paragraph{HOT} The highly optimized tolerance (HOT)~\cite{PhysRevLett.84.2529} model is introduced  using a ``forest fire'' example as follows: Suppose we have a forest which is prone to forest fires. Each portion of the forest has a different chance of starting the fire. We wish to minimize the damage by assigning (a limited amount of) resources such as firebreaks at different positions in the forest. More precisely, we have $n$ possible events, each with an associated probability $p_i, 1 \le i \le n$. Each event can lead to some loss $l_i$, which is a function of the resources $r_i$ allocated for that event $(l_i = f (r_i))$, whose total number is limited ($\sum_i r_i \le R$ for some given $R$). The aim is to minimize the expected cost $\sum_i p_i l_i$. The authors show that resource placement is related to the probability distribution $p_i$ by a power law and the probability of events which cause a loss greater than some value $k$ is related to $k$ by a power law too.
%
%
%\paragraph{R-MAT} The R-MAT (Recursive MATrix)~\cite{DBLP:conf/sdm/ChakrabartiZF04} model can be used to create graphs with community structure, power law degree distributions, and a small diameter. It generates weighted, directed and bipartite graphs. Graph generation is modeled with a matrix recursion -procedure in which the adjacency matrix (empty at the beginning) is recursively subdivided into four equal-sized partitions and edges are distributed across the partitions with unequal probabilities.

@@

At first we classify the generators on the basis of the respective application domains or user communities. The selected classes are not rigorously defined (e.g., they are not disjoint as we will show later), but they correspond to the currently most active research areas. Thus we believe that they form a natural first acquaintance for the reader.

In Tables~\ref{tab:comparisonCharacteristicsA},~\ref{tab:comparisonCharacteristicsB}   we overview the key characteristics of the data generators clustered according to the respective application domains. In particular, we show:

@@

\begin{sidewaystable}
\scriptsize
\centering
\tbl{Key characteristics of the generators (part A)} {
\begin{tabular}{| c | p{2.2cm} | p{2cm} |  p{2.2cm} | l |  l | l | p{3cm} | p{1.4cm} | l | }
 \hline
           &   & \multicolumn{2}{c}{\textbf{Domain}}
               & \multicolumn{2}{|c|}{\textbf{Operations}}
               & \multicolumn{4}{c|}{\textbf{Configuration}}
               \\ \hline
           &  \textbf{Generator}
               & \textbf{Type}
               & \textbf{Target / sample}
               & \textbf{Read}
               & \textbf{Update}
               & \textbf{\rot{Properties}}
               & \textbf{Distributions}
			   & \textbf{Output format}
               & \textbf{\rot{Distributed\ }}
               \\ \hline
\hline   % ====================== general graphs
\multirow{8}{*}{\rot{\textbf{General}}}
  & graph500  & fixed & & Y & N & Y & power-law & &  Y  \\
\cline{2-10}
   & R-MAt & fixed & & Y & N & Y & power-law & &  N  \\
\cline{2-10}
%  & Watts-Strogatz~\cite{watts1998collective} & fixed & & Y & N & Y &  & &  N  \\
%\cline{2-10}
  & Preferential Attachment~\cite{barabasi1999emergence} & fixed & & Y & N & Y &  & &  N  \\
\cline{2-10}
  & & & & & & & &  &   \\
\hline
\hline %  ======================  Semantic web
\multirow{22}{*}{\rot{\textbf{Semantic web}}}
 & LUBM & fixed & university  & fixed & N & Y & random (LCG) &  RDF & N   \\
\cline{2-10}
 & LBBM & extracted & Lehigh University BibTeX  & N & N & Y & Monte Carlo &  RDF & N   \\
\cline{2-10}
 & UOBM & fixed & university  & fixed & N & Y & random &  RDF & N   \\
\cline{2-10}
 & IIMB & fixed & movies  & N & N & Y & random &  RDF & N   \\
\cline{2-10}
 & BSBM & fixed & e-commerce  & fixed & N & Y & mostly normal &  RDF, relational & N   \\
\cline{2-10}
 & SP$^2$Bench & fixed & DBLP  & fixed & N & Y & based on DBLP  & RDF & N   \\
\cline{2-10}
 & \cite{Duan:2011:AOC:1989323.1989340} & extracted & -- & N & Y &N & -- &  RDF & N    \\
\cline{2-10}
 & DBPSB & extracted & DBpedia &  templates & N & Y & random &  RDF & N   \\
\cline{2-10}
 & LODIB & fixed & e-commerce &  N & N & Y & 44 types &  RDF & N   \\
\cline{2-10}
 & SIB & fixed & social network &  mixes & mix & Y & from real-world data &  RDF & N   \\
\cline{2-10}
 & Geographica & fixed & OpenStreetMap  & fixed + templates  & N & Y & -- &  RDF & N   \\
\cline{2-10}
 & WatDiv & schema-driven & user-defined  & templates & N & Y & uniform, normal, Zipfian &  RDF & N   \\
\cline{2-10}
 & RBench & extracted & DBLP, Yago  & templates & N & Y & from real-world data &  RDF & N  \\
\cline{2-10}
 & LDBC SPB & fixed & media  & mixes & N & Y & power law, skewed values, value correlation &  RDF & N  \\
\cline{2-10}
 & LinkGen & & & & & & & & \\
\hline
\end{tabular} }
\label{tab:comparisonCharacteristicsA}
\end{sidewaystable}

\begin{sidewaystable}
\scriptsize
\centering
\tbl{Key characteristics of the generators (part B)} {
\begin{tabular}{| c | p{2.2cm}| p{2cm} |  p{2.2cm} | l |  l | l | p{3cm} | p{1.4cm} | l | }
 \hline
           &   & \multicolumn{2}{c}{\textbf{Domain}}
               & \multicolumn{2}{|c|}{\textbf{Operations}}
               & \multicolumn{4}{c|}{\textbf{Configuration}}
               \\ \hline
           &  \textbf{Generator}
               & \textbf{Type}
               & \textbf{Target / sample}
               & \textbf{Read}
               & \textbf{Update}
               & \textbf{\rot{Properties}}
               & \textbf{Distributions}
			   & \textbf{Output format}
               & \textbf{\rot{Distributed\ }}
               \\ \hline
\hline  % ======================  graph databases
\multirow{7}{*}{\rot{\textbf{Graph DBs}}}
 & XGDBench & fixed  & social network  & fixed & Y & Y & power-law &  MAG &  Y  \\
 \cline{2-10}
& graphGen & pattern-driven (Cypher schema) & user-defined  & -- & -- & Y & -- &  property graphs & N   \\
 \cline{2-10}
 & gMark & schema-driven (internal schema) &  user-defined  & generated &  N  & Y & uniform, normal, zipfian &  N-triples & N    \\
\hline
\hline %  ======================   social networks
\multirow{9}{*}{\rot{\textbf{Social networks}}}
& LDBC SNB  & Y & Y &   generated &  & Y & Facebook-like &  CSV, RDF & Y     \\
\cline{2-10}
& S3G2 & Y & Y  & N &  & Y & Facebook-like  &  CSV, RDF & Y   \\
\cline{2-10}
& SNG  & Y & Y &   N &  & Y & power-law & ? &  ?   \\
\cline{2-10}
& Forest Fire  & N & Y   & N &  & N & power-law &  ? & N   \\
\cline{2-10}
& Darwini  & N & N &   N &  & N & user-defined &  ? & Y   \\
\cline{2-10}
& BTER  & N & N &   N &  & N & user-defined &  ? & Y  \\
\cline{2-10}
  & & & & & & & & &    \\
\cline{2-10}
  & & & & & & & & &    \\
\cline{2-10}
  & & & & & & & & &    \\
\hline
\hline   % ======================   graph analytics
\multirow{5}{*}{\rot{\textbf{Analytics}}}
  & & & & & & & & &    \\
\cline{2-10}
  & & & & & & & & &    \\
\cline{2-10}
  & & & & & & & & &    \\
\cline{2-10}
  & & & & & & & & &    \\
\cline{2-10}
  & & & & & & & &  &   \\
\hline
\hline   %  ======================  streaming
\multirow{5}{*}{\rot{\textbf{Streaming}}}
  & S2Gen & schema-driven & Social Network & Y & N & N & user-defined & RDF & N     \\
\cline{2-10}
  & RSPLab & schema-driven & Agnostic & Y & Y & N & user-defined & RDF & N     \\
\cline{2-10}
  & & & & & & & & &    \\
\cline{2-10}
  & & & & & & & & &    \\
\cline{2-10}
  & & & & & & & &  &   \\
\hline
\end{tabular} }
\label{tab:comparisonCharacteristicsB}
\end{sidewaystable}
